A holomorphic approach to branes in twisted~$M$-theory

### 2022-09-28 fivebranes/intro.tex
single edits

It is natural to wonder how this statement relates to more traditional formulations of the AdS/CFT correspondence, where local operators of the CFT are related to certain states of the gravitational theory on AdS. A precise relation will be articulated in section \ref{sec:states} where we argue that one can indeed understand $(\Obs_{grav}|_{Y})^{!}$ as a factorization algebra enhancement of the space of (twisted) multi-particle states of the gravitational theory on the backreacted geometry. Explicitly, this geometry refers to the manifold $X - Y$ obtained by subtracting the brane together with the data of a certain Maurer-Cartan element deforming the geometric structure used to define the gravitational theory on $X - Y$.

@@

  \item A system of twisted $D1-D5$ branes in a $T^{4}$-compactification of a twist of type IIB string theory. Upon compactifying along $T^4$ this can be understood as a variant of the above example where the deformed conifold is replaced by a certain superspace. The duality is understood as a twisted version of the duality between type IIB supergravity on $AdS_{3}\times S^{3}\times T^{4}$ and the symmetric orbifold CFT $Sym^{N}(T^{4})$.

@@

We propose similar statements at the level of the minimal twist. We fix a complex surface $X$ together with a pair of complex vector bundles $W, M \to X$ of ranks 2 and 1 respectively, satisfying the condition that $\wedge^{3}(W \oplus M) = \det X$. This condition ensures that $Tot (W\oplus M)$ is a Calabi-Yau 5-fold.

@@

The abelian six-dimensional $\cN=(2,0)$ theory is the worldvolume theory on a single fivebrane. 
It admits a field theoretic description as the so-called $\cN=(2,0)$ tensor multiplet. 
In \cite{SWtensor} an explicit description of the minimal, holomorphic, twist of this theory is given---it defines a complex three-dimensional factorization algebra that we will denote by $\Obs_1$.
In the main body of the paper, we show that this agrees with the factorization algebra we denoted $\Obs_{brane}(1)$ above. We emphasize that we only consider the classical limit of this factorization algebra in this paper. However as this is a free theory, there is a simple description of its quantization as a twisted enveloping algebra.\footnote{From the holographic point of view, this quantum parameter corresponds to including effects from the backreaction.}

Let us place this factorization algebra on the three-fold $Tot (M)$. Choosing a fiberwise hermitian metric affords a norm map \[\pi : Tot (M) \to \R_{+}\] whose fibers away from $0$ are the unit $S^{1}$ bundle in $M$. The pushforward $\pi_{*}\Obs_{1}$ is a stratified factoization algebra on the half-line. This may be thought of as a pair consisting of an associative algebra, which may be thought of as the algebra of modes of $\Obs_{1}$ along the five-manifold $Tot (M)$, together with a module for the algebra of modes.

In \cite{SWtensor} it is shown that in the case where $M$ is the trivial bundle, the naive dimensional reduction (where we discard higher Kaluza--Klein modes along the circle fiber) of this factorization algebra agrees with the factorization algebra associated to the minimal twist of five-dimensional $\cN = 2$ Yang--Mills theory on $\R\times M$ for the group $U(1)$ in perturbation theory around the zero instanton sector.

@@

\begin{conj}
The mode algebra $\pi_{*}\Obs_{1}|_{\R_{>0}}$ acts on $\cO (\operatorname{Higgs}^{W}_{GL(1)} X)$ where $\operatorname{Higgs}^{W}_{GL(1)} X$ denotes the moduli of $GL(1)$ Higgs bundles on $X$ whose higgs fields are $W[1]$-valued.
\end{conj}

@@

For a particular choice of $W, M, X$, we expect the superconformal element will deform the Hilbert space of the minimal twist in five dimensions to the equivariant cohomology of the moduli of abelian instantons on $\C^{2}$, and that the action of $\pi_{*}\Obs_{1}|_{\R_{>0}}$ compatibly deforms to the Heisenberg action studied by Grojnowski-Nakajima.
\subsection*{The $\cN=(2,0)$ theory of type $A_1$}

>>>>

It is natural to wonder how this statement relates to more traditional formulations of the AdS/CFT correspondence, where local operators of the CFT are related to certain states of the gravitational theory on AdS. A precise relation will be articulated in \S\ref{sec:states} where we argue that one can indeed understand $(\Obs_{grav}|_{Y})^{!}$ as a factorization algebra enhancement of the space of (twisted) multi-particle states of the gravitational theory on the backreacted geometry. Explicitly, this geometry refers to the manifold $X - Y$ obtained by subtracting the brane together with the data of a certain Maurer-Cartan element deforming the geometric structure used to define the gravitational theory on $X - Y$.

@@

  \item A system of twisted $D1-D5$ branes in a $T^{4}$-compactification of a twist of type IIB string theory. Upon compactifying along $T^4$ this can be understood as a variant of the above example where the deformed conifold is replaced by a certain superspace \cite{CP}. The duality is understood as a twisted version of the duality between type IIB supergravity on $AdS_{3}\times S^{3}\times T^{4}$ and the symmetric orbifold CFT $Sym^{N}(T^{4})$.

@@

We propose similar statements at the level of the minimal twist. 
We fix a complex surface $S$ together with a pair of complex vector bundles $L,W \to S$ of ranks $1$ and $2$ respectively, satisfying the condition that $X = \text{Tot} (L \oplus W)$ is a Calabi--Yau 5-fold.
The twisted eleven-dimensional supergravity lives on the eleven-manifold $\R \times X$.

@@

The abelian six-dimensional $\cN=(2,0)$ theory is also thought of as the worldvolume theory on a single fivebrane in $M$-theory. 
It admits a field theoretic description as the so-called $\cN=(2,0)$ tensor multiplet. 
In \cite{SWtensor} an explicit description of the minimal, holomorphic, twist of this theory is given.
At the level of this twist, the theory is defined on any complex three-fold (equipped with a square root of its canonical bundle). 
In this section, we consider the $\cN=(2,0)$ theory on the threefold $Y = \text{Tot}(L \to S)$ as a single fivebrane supported on the closed submanifold
\beqn
Y \hookrightarrow \R \times X .
\eeqn
We will denote the corresponding factorization algebra of observables on $Y$ by $\Obs_1$.

In the main body of the paper, we show that this agrees with the factorization algebra we denoted $\Obs_{brane}(1)$ above. We emphasize that we only consider the classical limit of this factorization algebra in this paper. However as this is a free theory, there is a simple description of its quantization as a twisted enveloping algebra.\footnote{From the holographic point of view, this quantum parameter corresponds to including effects from the backreaction.}

We place this factorization algebra on the three-fold $Y$ which is the total space of the line bundle $L \to S$. 
Choosing a fiberwise hermitian metric affords a norm map 
\[
\pi \colon Y \to \R_{+}
\] 
whose fiber away from $0$ is the total space of the unit sphere bundle.
The pushforward factorization algebra $\pi_{*}\Obs_{1}$ is a stratified factorization algebra on the non-negative half-line $\R_+ = \{t \geq 0\}$. 
We can tweak this factorization algebra slightly which gives rise to a constructible factorization algebra on $\R_+$.
In turn, this is equivalent to a pair of an associative algebra (which may be thought of as the algebra of modes of $\Obs_{1}$ along the five-manifold which is the total space of the unit sphere bundle) together with a module for this algebra.

In \cite{SWtensor} it is shown that in the case where $L$ is the trivial bundle, the naive dimensional reduction (where we discard higher Kaluza--Klein modes along the circle fiber) along 
\beqn
S \times \C \to S \times \R_+
\eeqn
agrees with the factorization algebra associated to the minimal twist of five-dimensional $\cN = 2$ supersymmetric Yang--Mills theory on $\R\times M$ for the group $U(1)$ in perturbation theory around the zero instanton sector.

@@

\begin{conj}
Let $\operatorname{Higgs}_{GL(1)} (S,L)$ denote the moduli space of $GL(1)$ Higgs bundles on the complex surface $S$ where the Higgs fields take values in the rank two bundle $W$.
The mode algebra $\pi_{*}\Obs_{1}|_{\R_{>0}}$ that we have just discussed acts on the space of functions on this moduli space
\beqn
\cO \left(\operatorname{Higgs}_{GL(1)} (S,L)\right) .
\eeqn
\end{conj}

@@

For a particular choice of $S,L,W$, we expect the superconformal element will deform the Hilbert space of the minimal twist in five dimensions to the equivariant cohomology of the moduli of abelian instantons on $\C^{2}$, and that the action of $\pi_{*}\Obs_{1}|_{\R_{>0}}$ compatibly deforms to the Heisenberg action studied by Grojnowski-Nakajima.

\subsection*{The $\cN=(2,0)$ theory of type $A_1$}
